%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{hyperref}
\usepackage{xcolor}

%------------------------------------------------

\name{Aleksey Valouev} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.


\address{(650)~$\cdot$~561~$\cdot$~5030 \\ valouev@berkeley.edu \\ Palo Alto, CA 94303} % Contact information

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	\textbf{University of California, Berkeley} \hfill \textit{August 2025 - May 2028} \\ 
	B.S. in Electrical Engineering \& Computer Science; GPA: 4.0/4.0 \smallskip \\
	Member, Machine Learning @ Berkeley \\
	Relevant Coursework: Data Structures \& Algorithms, Computer Architecture, Signal Processing
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{Berkeley AI Research Lab (BAIR)}{October 2025 - Present}{Researcher}{Berkeley, CA}
		\item Developing foundation computer vision models for fine-grained object detection in satellite imagery. Using multi-view vision transformers to jointly infer scene geometry and perform object detection.
		\item Supervised by Dr. Ritwik Gupta in the Darrell Computer Vision Group.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Machine Learning at Berkeley}{September 2025 - Present}{Machine Learning Engineer}{Berkeley, CA}
		\item Trained a vision language action (VLA) model to autonomously pilot a lunar lander in an OpenAI gym environment.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Boston University Computational Imaging Systems Lab}{July 2024 - August 2024}{Research Intern}{Boston, MA}
		\item Combined 3-D scene representation (NeRF) with Fourier optics to pioneer a versatile and adaptive approach to extended depth microscopy. Developed a lightweight and versatile tool for miniaturized imaging of live rodent brains.
		\item First-author publication in IEEE (\textcolor{blue}{\href{https://ieeexplore.ieee.org/document/10959478}{https://ieeexplore.ieee.org/document/10959478}}).
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{University of Southern California, Marshall School of Business}{May 2022 - June 2024}{Research Assistant}{Los Angeles, CA}
		\item Aggregated, preprocessed, and analyzed short seller tweets and corporate disclosures to predict short squeeze attacks.
		\item Performed textual analysis of published papers using NLP techniques. Presented results at the USC CETAFE Conference.
		\item Acknowledged in a journal publication (\textcolor{blue}{\href{https://dx.doi.org/10.2139/ssrn.3849581}{https://dx.doi.org/10.2139/ssrn.3849581}}).
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS AND LEADERSHIP
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects and Leadership}

	\begin{rSubsection}{Machine Learning for Wildfire Prediction}{September 2021 - December 2022}{}{}
		\item Acquired and processed satellite and sensor data using Geographic Information System (GIS) tools, Pandas, and Numpy.
		\item Used logistic regression and random forest models with time series data to predict monthly wildfire risk at 5 kilometer resolution.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{AI-Powered Network of Sensors for Real-Time Wildfire Detection}{January 2023 - June 2025}{}{}
		\item Created a novel Intelligent Wireless Sensing Network (IWSN) for real-time wildfire detection using CV on IoT devices.
		\item Provisional patent for the IWSN registered with the US Patent Office. Worked on deployment in the Santa Cruz Mountains.
	\end{rSubsection}

\end{rSection}

\begin{rSection}{Skills and Volunteering}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Technical & Python, Java, PyTorch, Matplotlib, Yahoo Finance API, Stanford Named Entity Recognizer, NLP \\
		Volunteering & Supervisor at Palo Alto High School robotics summer camp. Outreach with National Geographic. \\
		Linkedin & \textcolor{blue}{\href{https://www.linkedin.com/in/aleksey-valouev/}{https://www.linkedin.com/in/aleksey-valouev/}}
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

	%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
